A Neural Network Alternative to Convolutive Audio Models for Source Separation

### 2017-06-10 paper/paper.tex
Add files via upload

@@

Having obtained the contributions of the sources (separated spectrograms), the next step is to transform these spectrograms back into the time domain. This is given as,
\begin{equation}
    x_{i}(t) = \text{STFT}^{-1}\left(\frac{\mathbf{X_{i}}}{\sum_{i}\mathbf{X}_{i}}\odot \mathbf{X}_{m} \odot e^{i\Phi_{m}}\right)~\text{for}~i\in\{1, 2\}
\end{equation}
Here $x_{i}(t)$ denotes the separated speech signal in time and $\Phi_{m}$ represents the phase of the mixture. Also, $\odot$ represents the element-wise multiplication operation and the division is also element-wise.

\section{Experiments}
\label{sec:experiments}
We now describe the experiments used to evaluate our auto-encoder based convolutive audio models. We do so by comparing the separation performance of these models to the neural network based models proposed in~\cite{}(**ICASSP paper**). For a uniform experimental setup, we apply a separation scheme described in~\ref{sec:ss} to both the models. We compare the performance in terms of median BSS\_eval metrics~\cite{}(**BSS eval paper**) viz., signal-to-distortion (SDR), signal-to-interference (SIR) and signal-to-artifact ratio (SAR) parameters. We also compare the median intelligibility scores in terms of the STOI index~\cite{}(**STOI paper**). To compare these models, we use the TIMIT corpus~\cite{} (**Timit reference**). To form these mixtures, we randomly select a pair of male-female speakers from the TIMIT corpus. Of the $10$ utterances available for each speaker, one utterance is randomly selected for each speaker. These two selected utterances are mixed at $0 dB$ to generate the testing mixture. For the evaluation, we generate $20$ such mixtures and compare the models for different parameter configurations. As the pre-processing step, we apply a $1024$ point short-time Fourier transform representation with a hop of $25\%$. The magnitude spectrogram is then given as an input to the network.

@@

\subsection{Experimental setup}
\label{subsec:setup}

>>>>

\begin{figure}[t]
\centering
  \includegraphics[clip, trim = 0cm 0cm 0cm 0cm, width=\linewidth]{Figs/CNN_demo.png}
  \caption{...}~\label{fig:cnn_demo}
\end{figure}

@@

Having obtained the contributions of the sources (separated spectrograms), the next step is to transform these spectrograms back into the time domain. This is given as,
\begin{equation}
    x_{i}(t) = \text{STFT}^{-1}\left(\frac{\mathbf{X_{i}}}{\sum_{i}\mathbf{X}_{i}}\odot \mathbf{X}_{m} \odot e^{i\Phi_{m}}\right)~\text{for}~i\in\{1, 2\}
\end{equation}
Here $x_{i}(t)$ denotes the separated speech signal in time and $\Phi_{m}$ represents the phase of the mixture and $\text{STFT}^{-1}$ is the inverse short-time Fourier transform operation that transforms the complex spectrogram into its corresponding time domain representation. Also, $\odot$ represents the element-wise multiplication operation and the division is also element-wise.

\begin{figure*}[ht!]
\centering
  \includegraphics[clip, trim = 0cm 0cm 0cm 0cm, width=\linewidth]{Figs/SeparationPerformance.png}
  \caption{...}~\label{fig:separation_performance}
\end{figure*}

\section{Experiments}
\label{sec:experiments}
We now describe the experimental setup used to evaluate our auto-encoder based convolutive audio models. We do so by comparing the separation performance of these models to the neural network based models proposed in~\cite{}(**ICASSP paper**). For a uniform experimental setup, we apply a separation scheme described in~\ref{sec:ss} to both the models. We compare the performance in terms of median BSS\_eval metrics~\cite{}(**BSS eval paper**) viz., signal-to-distortion (SDR), signal-to-interference (SIR) and signal-to-artifact ratio (SAR) parameters. We also compare the median intelligibility scores in terms of the STOI index~\cite{}(**STOI paper**). To compare these models, we use the TIMIT corpus~\cite{} (**Timit reference**). To form these mixtures, we randomly select a pair of male-female speakers from the TIMIT corpus. Of the $10$ utterances available for each speaker, one utterance is randomly selected for each speaker. These two selected utterances are mixed at $0 dB$ to generate the testing mixture. For the evaluation, we generate $20$ such mixtures and compare the models for different parameter configurations. As the pre-processing step, we apply a $1024$ point short-time Fourier transform representation with a hop of $25\%$. The magnitude spectrogram is then given as an input to the network.

@@
